Supplmental Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-03-01 Ben_Manuscripts/structure_paper/supplemental.tex
removed unneeded files

		\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to
		have a test system with an intial spacing below the experimental value. As soon
		as the restraining potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the
		columns are able to repel resulting in a large jump in pore spacing
		(Figure~\ref{fig:p2p_39}). After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
		There is a large uncertainty in this value because the 1-4 pore spacing
		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
		spacings is 3.96 nm. The system deviates from hexagonal geometry and is trending
                towards cubic packing.

		\item 41 \AA~: We chose to test a pore spacing of 41 \AA~since
		it closely matches the experimental pore spacing. Again, we observe abrupt
		repulsion of columns once the restraining potential is switched to 56 KJ
		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). After 400 ns, the
		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
		spacings is 3.96 nm.

		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger
		than the experimental value. We observe relatively stable pore spacing during
		the restrained portion of the dry equilibration procedure
		(Figure~\ref{fig:p2p_45}). The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
		The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
		pore spacing. We chose to use this value for all our simulations in the main
		text.

		\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \% larger than the
		experimental value. Once the restraining potential reaches 56 KJ mol$^{-1}$
		nm$^{-2}$, the pore spacing begins to decrease linearly (Figure~\ref{fig:p2p_50}).
		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm. There is a large
                uncertainty with this value because, again, the array of pores deviates from 
                hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
                2 drifts outward from the array and forces the 1-4 distance to shrink in 
                response.

		\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
		a distance where monomers in each pore no longer intersect adjacent pores. Once
		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle when the force constants are
		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
		avoiding a system such as this where vacuum gaps between pore columns are
		introduced unnecessarily. The system equilibrates to a pore spacing of 4.27
		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
                spacing of 3.99 \AA~ which distorts the hexagonal array.

>>>>

		\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to
		have a test system with an intial spacing below the experimental value. As soon
		as the restraining potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the
		columns are able to repel resulting in a large jump in pore spacing
		(Figure~\ref{fig:p2p_39}). %After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
%		There is a large uncertainty in this value because the 1-4 pore spacing
%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
%		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
%		spacings is 3.96 nm. The system deviates from hexagonal geometry and is trending
%                towards cubic packing.

		\item 41 \AA~: We chose to test a pore spacing of 41 \AA~since
		it closely matches the experimental pore spacing. Again, we observe abrupt
		repulsion of columns once the restraining potential is switched to 56 KJ
		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). %After 400 ns, the
%		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
%		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
%		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
%		spacings is 3.96 nm.

		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger
		than the experimental value. This systems exhibits the smallest response to our 
 		equilibration procedure (Figure~\ref{fig:p2p_45}) and we chose to use this
                value for all our simulations in the main text.
f		%The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
		%The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
		%pore spacing. We chose to use this value for all our simulations in the main
		%text.

		\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \%
		larger than the experimental value. Once the restraining potential reaches 56
		KJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
		a linear trend (Figure~\ref{fig:p2p_50}).
%		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm.
%		There is a large
 %               uncertainty with this value because, again, the array of pores deviates from 
 %               hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
  %              2 drifts outward from the array and forces the 1-4 distance to shrink in 
   %             response.

		\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
		a distance where monomers in each pore no longer intersect adjacent pores. Once
		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle when the force constants are
		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
		avoiding a system such as this where vacuum gaps between pore columns are
		introduced unnecessarily. %The system equilibrates to a pore spacing of 4.27
%		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
 %               spacing of 3.99 \AA~ which distorts the hexagonal array.
